Two-Dimensional Vesicle Hydrodynamics from Hydrophobic Attraction Potential

### 2021-09-30 doc/main_jfm.tex
adding acknowledgments
yny acknowledgement

\begin{acknowledgments}
%We would like to acknowledge 
\end{acknowledgments}

>>>>

\begin{acknowledgments}
  {\bf Acknowledgments:} B.Q.~acknowledges support from NSF (Grant
  No.~DMS 2012560) and from the Simons Foundation, Mathematics and
  Physical Sciences-Collaboration Grants for Mathematicians (Award
  No.~527139). Y.-N. Y.~acknowledges support from NSF (Grant No.~DMS 1614863 and 1951600) and
  Flatiron Institute, part of Simons Foundation.
%We would like to acknowledge 
\end{acknowledgments}
